Prefetching SPARQL query cacher

### 2016-05-25 dissertation/cache-proxy.tex
comment on orthogonality

It would also be advantageous to design the experiment so that a
combination of factors would correspond to the null hypothesis,
i.e. that the proxy was not in use and the remote endpoint would
tackle the whole load. To achieve this, a fractional factorial
experiment would likely result where certain combinations would be
banned. I did not think this complete through to a concrete
experiment.

>>>>

It would also be advantageous to design the experiment so that a
combination of factors would correspond to the null hypothesis,
i.e. that the proxy was not in use and the remote endpoint would
tackle the whole load. I did not think this complete through to a
concrete experiment, but it might be a challenging problem to maintain
orthogonality, i.e. ensure that all level combinations can occur in
the same number of runs.
